Simple and robust inference of connectomes using partial correlation coefficients

### 2014-06-10 article.tex
make more precision

The connectivity network to infer is only made of direct relationships
which defined relation between neurons that still exists when
conditioned on all other neurons. In other words, there is not intermediary
between those two neurons. Under the hypothesis that neurons follow a jointly
Gaussian distribution $p_{\mathcal{X}_1, \dots, \mathcal{X}_p} \sim
\mathcal{N}(\mu; \Sigma)$, two neurons $\mathcal{X}_i$ and $\mathcal{X}_j$ are
independent $\mathcal{X}_i\perp \mathcal{X}_j$ if the Pearson correlation
coefficient $\rho_{X_iX_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii}
\Sigma_{jj}}} = 0,$ and are conditionally independant to all others neurons
$\mathcal{X}_i \perp \mathcal{X}_j |\mathcal{V}^{i,j}$ if the partial
correlation coefficient (of order $p-2$) $\rho_{X_i, X_j | \mathcal{V}^{i,j}}
= \frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}} = 0$,
where $\Sigma^{-1}$ is the inverse of the covariance matrix.
Therefore, by definition, the partial correlation coefficient between two
neurons only estimates the direct relationship between them.

>>>>

The connectivity network to infer is only made of direct relationships
which defined relation between neurons that still exists when
conditioned on all other neurons. In other words, there is not intermediary
between those two neurons. Under the hypothesis that neurons follow a jointly
Gaussian distribution $p_{\mathcal{X}_1, \dots, \mathcal{X}_p} \sim
\mathcal{N}(\mu; \Sigma)$, two neurons $\mathcal{X}_i$ and $\mathcal{X}_j$ are
independent $\mathcal{X}_i\perp \mathcal{X}_j$ if the Pearson correlation
coefficient $\rho_{X_iX_j} = \frac{\Sigma_{ij}}{\sqrt{\Sigma_{ii}
\Sigma_{jj}}} = 0,$ and are conditionally independant to all others neurons
$\mathcal{X}_i \perp \mathcal{X}_j |\mathcal{V}^{i,j}$ if the partial
correlation coefficient (of order $p-2$) $\rho_{X_i, X_j | \mathcal{V}^{i,j}}
= \frac{\Sigma^{-1}_{ij}}{\sqrt{\Sigma^{-1}_{ii} \Sigma^{-1}_{jj}}} = 0$,
where $\Sigma^{-1}_$ is the inverse of the covariance matrix.
Therefore, by definition, the partial correlation coefficient between two
neurons only estimates the direct relationship between them.
